SoK: Application Attack Defenses (in Question)

### 2014-10-07 docs/questioning.tex
some rephrasing
more fixes

Note that the calculations are carried out vertically; the ratio of
attack events to normal events does not enter into sensitivity and
specificity. This is what allows us to derive them based on test data,
without using data from a real production environment. At the same
time, however, this is what limits their usefulness. When we obtain a
test result in a production environment, be it negative or positive,
we really want to know how much we should be worried. In other words,
if an attack is detected in a production environment, how much should
we be worried? If no attack is detected in a production environment,
how relaxed should we be that no attack has indeed taken place?

@@

This time the ratios are taken horizontally; the ratio of attacks to
innocuous events affects the calculations. In fact, if PR is the real
probability that an attack happens, the prevalence, then we
have~\cite{linn2004,altman1994}:

>>>>

Note that the calculations are carried out vertically in
Table~\ref{tab:sensitivity-specificity}; the ratio of attack events to
normal events does not enter into sensitivity and specificity. This is
what allows us to derive them based on test data, without using data
from a real production environment. At the same time, however, this is
what limits their usefulness. When we obtain a test result in a
production environment, be it negative or positive, we really want to
know how much we should be worried, or relaxed. In other words, if an
attack is detected in a production environment, how much should we be
worried? If no attack is detected in a production environment, how
relaxed should we be that no attack has indeed taken place?

@@

This time the ratios are taken horizontally; the ratio of attacks to
innocuous events affects the calculations. In fact, if PR is the
probability of attacks in the real world, the prevalence, then we
have~\cite{linn2004,altman1994}:
